Development of a educational and sustainable robotic platform for children and adults

### 2013-11-02 doc/paper.tex
autocommited by makefile

Each board can be individually programmed using the freely available Arduino IDE having the Robot connected to the computer using an USB cable. The system is powered using four rechargeable NIMH-batteries which can be recharged on the board by connecting an appropriate power source to the barrel jack on board.

\begin{table}[h!]
\centering
\begin{tabular}{p{0.2\textwidth}p{0.2\textwidth}p{0.6\textwidth}}
\toprule
Assessment Criteria    & Rating & Description \\
\midrule
Affordable      & \stars{2}    & With a price tag of 189 Euro the Arduino Robot is far above the price limit of 100 Euro. The price for the basic robot is very high compared to the features.\\
Educational     & \stars{3}     & The Arduino robot comes pre-built and therefore lacks the build experience. Learning material for teachers is not provided but instructions for other Arduino products are easily adapted to the robots system.\\
Sustainable       & \stars{4}     &  \\
Extendable & \stars{5}      &  \\
Trouble-free & \stars{4} & Since the Arduino robot comes pre-assembled and tested in factory, the robot can be called trouble-free. Uploading new code using the Arduino IDE works well on every officially supported operating system.\\
Open-Source & \stars{3} & Even though it is claimed that the Arduino robot is open-source, not all files required for building the robot are published. The website is missing the PCB design files and includes the schematics only. A software library is available under a open-source license.  \\
\bottomrule
\end{tabular}
\caption{Arduino Robot evaluation}
\label{tbl:arduinorobot_eval}
\end{table}

@@

\begin{table}[h!]
\centering
\begin{tabular}{llr}
\toprule
Assessment Criteria    & Rating & Description \\
\midrule
Affordable      & \stars{2}    & 13.65      \\
Educational     & \stars{4}     & 92.50      \\
Sustainable       & \stars{3}     & 33.33      \\
Extendable & \stars{2}      & 8.99       \\
Open-Source & \stars{4} & bar \\
\bottomrule
\end{tabular}
\caption{Lego Mindstorms evaluation}
\label{tbl:mindstorms_eval}
\end{table}

>>>>

Each board can be individually programmed using the freely available Arduino IDE having the Robot connected to the computer using an USB cable. The IDE provides a lot of examples for the robot platform and introduces a library for abstract access to the robots functionaly. Power is applied to the system using four rechargeable NIMH-batteries which can be directly recharged on the board by connecting an appropriate power source to the board.

The robot can interact with its environment using movement generated by two controllable DC motors attached to wheels and stabilized using two ball caster. In addition to movement the robot can play sounds using a small speaker on the control board and display text and images on the display mounted on the control board as well. In contrast to the actuators the user can interact with the robot using buttons and several sensors such as infrared sensors for line following tasks or distance measurement.

\begin{table}[h!]
\centering
\begin{tabular}{p{0.2\textwidth}p{0.2\textwidth}p{0.6\textwidth}}
\toprule
Assessment Criteria    & Rating & Description \\
\midrule
Affordable      & \stars{2}    & With a price tag of 189 Euro the Arduino Robot is far above the price limit of 100 Euro. The price for the basic robot is very high compared to its features.\\
Educational     & \stars{3}     & The Arduino robot comes pre-built and therefore lacks the build experience. Learning material for teachers is not provided but a lot of examples and a library to ease programming is provided. Instructions for other Arduino products can be easily adapted to the robot. \\
Sustainable       & \stars{4}     &  The robot is ROHS certified and contains no hazardous components. The integrated charging circuit for the NIMH batteries eliminates the need of a dedicated battery charger and therefore reduces the amount of electrical waste. A small restraint is the choice of components because they cannot be interchanged/repaired by beginners. This is due to the manufacturing process which requires SMD components to be cost effective. Through hole parts would be easier to interchange but require manual assembly which is very expensive.\\
Extendable & \stars{5}      &  Having prototyping areas directly on the control board, the robot can be considered extendable. Moreover connectors for additional sensors are populated all over the robot board making it possible and easy to add sensors without soldering.\\
Trouble-free & \stars{4} & Since the Arduino robot comes pre-assembled and tested in factory, the robot can be called trouble-free. Transportation defects like loose screws can be repaired using household items. Uploading new code using the Arduino IDE works well on every officially supported operating system.\\
Open-Source & \stars{3} & Even though it is claimed that the Arduino robot is open-source, not all files required for building the robot are published. The website is missing the PCB design files and includes the schematics only. A software library is available under a open-source license. \\
\bottomrule
\end{tabular}
\caption{Arduino Robot evaluation}
\label{tbl:arduinorobot_eval}
\end{table}

To sum it up the Arduino robot is an extendable robot platform which requires no assembly at all. The integrated battery charging makes it a sustaina ble robot but the high price reduces the overall rating to an average of 3.5 stars.

@@

\begin{table}[h!]
\centering
\begin{tabular}{llr}
\toprule
Assessment Criteria    & Rating & Description \\
\midrule
Affordable      & \stars{2}    & 13.65      \\
Educational     & \stars{4}     & 92.50      \\
Sustainable       & \stars{3}     & 33.33      \\
Extendable & \stars{2}      & 8.99       \\
Trouble-free & \stars{5} & \\
Open-Source & \stars{4} & bar \\
\bottomrule
\end{tabular}
\caption{Lego Mindstorms evaluation}
\label{tbl:mindstorms_eval}
\end{table}
